\begin{longtable}{Xr}
	Yi-Hao Peng. ``Making Lectures Non-Visually Accessible'' & Summer 2020 \\
	Incoming Graduate, CMU. &  \\
	\\

	Joon Jang. ``Understanding and Improving Presentation Accessibility'' & Spring/Summer 2020 \\
	Undergraduate, CMU. &  \\
	\\

	Xingyu (Bruce) Liu. ``Automated Metrics for Predicting Video Accessibility'' & Spring/Summer 2020 \\
	Undergraduate, CMU. Next: UCLA PhD student. &  \\
	\\

	Junhan (Judy) Kong. ``Generating AR Tutorials by Demonstration'' & Spring 2020 \\
	Undergraduate, CMU. Next: UW PhD student. &  \\
	\\

	Kimberly Do. ``How does expertise impact video description?'' & Summer 2020 \\
	Undergraduate, Georgia Tech (REU program). &  \\
	\\

	Annika Esau. ``Can we control dialog generation using scripts?'' & Summer 2020 \\
	Undergraduate, University of Idaho (REU program). &  \\
	\\

	Dena Sabha. ``Generating AR Tutorials'' & Summer 2020 \\
	Undergraduate, UW (REU program). &  \\
	\\

	Christina Low. ``Making Social Media Images Accessible'' & Summer 2019 \\
	Undergraduate, Stony Brook University (REU program). &  \\
	\\

	Emma McCamey. ``Making Social Media Images Accessible'' & Summer 2019 \\
	Undergraduate, Virginia Commonwealth University (REU program). &  \\
	\\

	Tonya Nguyen. ``SlideSpecs: Collaborative Presentation Feedback'' & Fall 2018 \\
	Undergraduate, UC Berkeley. Next: UC Berkeley PhD student. &  \\
	\\

	Kaushik Kasi. ``Detecting Slide Transitions for Facilitating Feedback'' & Spring 2018 \\
	Undergraduate, UC Berkeley. Next: Apple. &  \\
	\\

	Vivian Liu. ``How is food represented on Instagram?'' & Fall 2016 \\
	Undergraduate, UC Berkeley. Next: Columbia PhD student. &  \\
	\\

\end{longtable}