\begin{longtable}{Xr}
	``Accessible Creativity.'' \textit{Apple Workshop on Human Centered Machine Learning}. Cupertino, CA. & Summer 2024 \\
	\\

	``Human-AI Interaction (Invited discussant).'' \textit{Human-Computer Interaction Consortium (HCIC)}. Delevan, WI. & Summer 2024 \\
	\\

	``Accessible Creativity with Generative AI.'' \textit{UC Irvine Workshop on Accessible Work and Generative AI}. Irvine, CA. & Summer 2024 \\
	\\

	``Generative AI for Accessible Creativity.'' \textit{Adobe HCI Seminar}. San Francisco, CA. Presented virtually. & Spring 2024 \\
	\\

	``The Promise and Peril of using Generative AI for Accessibility.'' \textit{UT iSchool Colloquium}. Austin, TX. & Fall 2023 \\
	\\

	``Invited guest.'' \textit{Fairness in Datasets for Machine Learning in Accessibility Workshop}. Virtual Event. & Summer 2023 \\
	\\

	``Accessible Creativity with Generative AI.'' \textit{AIST Creative HCI Seminar}. Tokyo, Japan. Presented virtually. & Spring 2023 \\
	\\

	``Panelist (Computer Vision for Media Accessibility; Natural Language Processing for Media Accessibility).'' \textit{WAI-CooP’s AI and Accessibility Research Symposium}. Virtual Event. & Winter 2023 \\
	\\

	``Human AI Systems for Making Media Accessible.'' \textit{Marquette CS Colloquium}. Virtual Event. & Fall 2022 \\
	\\

	``The Job Search: Applicant's View.'' \textit{EECS Rising Stars}. Austin, TX. & Fall 2022 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{MIT HCI Seminar}. Cambridge, MA. Presented virtually. & Spring 2022 \\
	\\

	``Video Accessibility.'' \textit{Stanford HCI Seminar}. Stanford, CA. Presented virtually. & Spring 2022 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{Carnegie Mellon University HCII}. Pittsburgh, PA. & Winter 2021 \\
	\\

	``XR Access Research Panelist'' \textit{XR Access Symposium}. Virtual Event. & Summer 2021 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{Cornell University}. Virtual Event. & Spring 2021 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{École Polytechnique Fédérale de Lausanne (EPFL)}. Virtual Event. & Spring 2021 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{University of Texas, Austin}. Virtual Event. & Spring 2021 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{University of Southern California}. Virtual Event. & Spring 2021 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{University of Pennsylvania}. Virtual Event. & Spring 2021 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{Johns Hopkins University}. Virtual Event. & Spring 2021 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{University of Maryland, College Park}. Virtual Event. & Spring 2021 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{Emory University}. Virtual Event. & Spring 2021 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{University of Utah}. Virtual Event. & Spring 2021 \\
	\\

	``Human AI Systems for Making Videos Useful.'' \textit{Adobe Research}. Virtual Event. & Spring 2021 \\
	\\

	``Describing Videos.'' \textit{CMU HCII Seminar}. Pittsburgh, PA. & Summer 2020 \\
	\\

	``Generating Anti-scam Dialogue.'' \textit{DARPA PI Meeting}. Washington, DC. & Spring 2020 \\
	\\

	``Text-based Video Navigation.'' \textit{Apple}. Seattle, WA. & Summer 2019 \\
	\\

	``Text-based Video Navigation.'' \textit{CMU Course: Human-AI Interaction}. Pittsburgh, PA. & Fall 2019 \\
	\\

	``What is HCI?'' \textit{UC Berkeley Course: CS 10}. Berkeley, CA. & Spring 2019 \\
	\\

	``What is HCI?'' \textit{UC Berkeley Course: CS 10}. Berkeley, CA. & Fall 2018 \\
	\\

	``SceneSkim: Searching and Browsing Movies Using Synchronized Captions, Scripts and Plot Summaries.'' \textit{LAUC-B conference: ``Focus on the Visual: Digital Humanities and Libraries''}. Berkeley, CA. & Spring 2016 \\
	\\

	``SceneSkim: Searching and Browsing Movies Using Synchronized Captions, Scripts and Plot Summaries.'' \textit{Pixar}. Emeryville, CA. & Fall 2015 \\
	\\

	``Video Digests: A Browsable, Skimmable Format for Informational Lecture Videos.'' \textit{BEARS at UC Berkeley}. Berkeley, CA. & Fall 2014 \\
	\\

	``SceneSkim: Searching and Browsing Movies Using Synchronized Captions, Scripts and Plot Summaries.'' \textit{UC Berkeley Course: NWMEDIA 190: Making Sense of Cultural Data}. Berkeley, CA. & Spring 2014 \\
	\\

	``Automatically Extracting Command Names from Online Tutorials.'' \textit{UC Berkeley Visual Computing Lab Retreat}. Bodega Bay, CA. & Fall 2011 \\
	\\

\end{longtable}