\begin{longtable}{Xr}
	\textbf{Sumaya Al-Bedaiwi}. ``Assessment Support for Speech Languge Pathologists (Master's Thesis).'' & Fall 2024 - Present \\
	5-Year Master's Student, UT Austin &  \\
	\\

	\textbf{Katie Clark}. ``2D Images to Tactile Graphics (Master's Thesis).'' & Fall 2024 - Present \\
	5-Year Master's Student, UT Austin &  \\
	\\

	\textbf{Sarah Zheng}. ``Describing Scientific Diagrams (Honors Thesis).'' & Fall 2024 - Present \\
	Undergraduate Student, UT Austin &  \\
	\\

	\textbf{Elin Park}. ``Audio Production for d/Deaf and Hard of Hearing Creators (Independent Study).'' & Fall 2024 - Present \\
	Undergraduate Student, UT Austin &  \\
	\\

	\textbf{Jerry He}. ``Optimizing Sensor Position for Aiming (Independent Study).'' & Fall 2024 \\
	Undergraduate Student, UT Austin &  \\
	\\

	\textbf{Akhil Iyer}. ``Automatic Live Descriptions (co-author CHI 2024).'' & Fall 2023 - Present \\
	Undergradaute, UT Austin. &  \\
	\\

	\textbf{Adi Barua}. ``Creating Short Videos from Long Videos (first author IUI 2024, Honors Thesis).'' & Fall 2023 - Present \\
	Undergradaute, UT Austin. &  \\
	\\

	\textbf{Ananya Gubbi Mohanbabu}. ``Context-Aware Descriptions (first author ASSETS 2024 paper and Master's Thesis).'' & Fall 2023 - Spring 2024 \\
	Master's Student, UT Austin. Next: PhD at UT Austin &  \\
	\\

	\textbf{Hansika Murugu}. ``Evaluating Long Form Answers to Visual Questions (Independent Study).'' & Fall 2023 - Spring 2024 \\
	Undergradaute at HKUST, Visiting UT Austin. Next: MS at UMD &  \\
	\\

	\textbf{Ujjaini Das}. ``Describing Complex Motion (Independent Study).'' & Fall 2023 - Spring 2024 \\
	Undergradaute, UT Austin. &  \\
	\\

	\textbf{Tess Van Deaele}. ``Making Short Videos Accessible (first-author CHI 2024 and Honors Thesis)'' & Fall 2022 - Spring 2023 \\
	Undergradaute, UT Austin. Next: Software Engineer at Verkada &  \\
	\\

	\textbf{Yuning Zhang}. ``Making Short Videos Accessible (co-author CHI 2024).'' & Spring 2023 \\
	Undergradaute, UT Austin. Next: MS at Cornell &  \\
	\\

	\textbf{Jalyn Derry}. ``Making Short Videos Accessible (co-author CHI 2024).'' & Spring 2023 \\
	Undergradaute, UT Austin. Next: UX Design at Expedia &  \\
	\\

	\textbf{Pranav Venkatesh}. ``Comparing Web and LLM Search (Independent Study, Co-Advised with Eunsol Choi).'' & Fall 2022 - Fall 2023 \\
	Undergradaute, UT Austin. &  \\
	\\

	\textbf{Doeun Lee}. ``Comparing Web and LLM Search (Independent Study, Co-Advised with Eunsol Choi).'' & Fall 2022 - Fall 2023 \\
	Undergradaute, UT Austin. Next: Master's at OSU &  \\
	\\

	\textbf{Daniel Killough}. ``Community-Driven Live Descriptions (first author ASSETS 2023).'' & Summer 2022 - Spring 2023 \\
	Undergradaute, UT Austin. Next: PhD at University of Wisconsin Madison &  \\
	\\

	\textbf{Yi-Hao Peng}. ``Making Lectures Non-Visually Accessible'' & Summer 2020 \\
	Incoming Graduate, CMU. &  \\
	\\

	\textbf{Joon Jang}. ``Understanding and Improving Presentation Accessibility'' & Spring/Summer 2020 \\
	Undergraduate, CMU. &  \\
	\\

	\textbf{Xingyu (Bruce) Liu}. ``Automated Metrics for Predicting Video Accessibility'' & Spring/Summer 2020 \\
	Undergraduate, CMU. Next: UCLA PhD student. &  \\
	\\

	\textbf{Junhan (Judy) Kong}. ``Generating AR Tutorials by Demonstration'' & Spring 2020 \\
	Undergraduate, CMU. Next: UW PhD student. &  \\
	\\

	\textbf{Kimberly Do}. ``How does expertise impact video description?'' & Summer 2020 \\
	Undergraduate, Georgia Tech (REU program). &  \\
	\\

	\textbf{Annika Esau}. ``Can we control dialog generation using scripts?'' & Summer 2020 \\
	Undergraduate, University of Idaho (REU program). &  \\
	\\

	\textbf{Dena Sabha}. ``Generating AR Tutorials'' & Summer 2020 \\
	Undergraduate, UW (REU program). &  \\
	\\

	\textbf{Christina Low}. ``Making Social Media Images Accessible (co-author CHI 2020)'' & Summer 2019 \\
	Undergraduate, Stony Brook University (REU program). &  \\
	\\

	\textbf{Emma McCamey}. ``Making Social Media Images Accessible (co-author CHI 2020)'' & Summer 2019 \\
	Undergraduate, Virginia Commonwealth University (REU program). &  \\
	\\

	\textbf{Tonya Nguyen}. ``SlideSpecs: Collaborative Presentation Feedback (co-author IUI 2023)'' & Fall 2018 \\
	Undergraduate, UC Berkeley. Next: UC Berkeley PhD student. &  \\
	\\

	\textbf{Kaushik Kasi}. ``Detecting Slide Transitions for Facilitating Feedback'' & Spring 2018 \\
	Undergraduate, UC Berkeley. Next: Apple. &  \\
	\\

	\textbf{Vivian Liu}. ``How is food represented on Instagram?'' & Fall 2016 \\
	Undergraduate, UC Berkeley. Next: Columbia PhD student. &  \\
	\\

\end{longtable}